Exploration

### 2018-03-01 exploration.Rmd
added IPMpack seed bank

## Species description: Life history, characteristics, relevant attributes
The simulated species is fully described here. The object `sp_i` is a list containing elements for the global parameters, relationships with environmental variables, and demographic matrices that are applicable or potentially applicable for that modeling strategy. Parameters are abbreviated with the associated kernel component (e.g., `s_*` for survival, `g_*` for growth, etc) and the type of covariate (`*_z` for size, `*_x` for environmental covariates).
```{r sp_i}
#set.seed(20)
subsamp <- NA
mean_abund <- 500
regPlots <- F
ipmPlots <- F
if(is.na(subsamp)) { cells <- 1:n_distinct(lc.df$CellID)
} else { cells <- sample(1:n_distinct(lc.df$CellID), subsamp, replace=FALSE) }
n.cell <- length(cells)
n_i <- rpois(n.cell, mean_abund)
sp_i <- list(p=list(s_z=c(-1.75, .75), # b1 + b2*z
                    s_x=c(1, -.1, -.5, -.1), # b1*x1 + ...
                    g_z=c(.2, 2, -0.1), # b1 + b2*z + b3*z^2
                    g_x=c(1, -.1, 1.5, -.1), #b1*x1 + ...
                    g_sig=1, # growth ~ N(E, g_sig)
                    fl_z=c(-1.5, .1, .1), # b1 + b2*z + b3*z^2 + b4*z^3
                    fl_x=c(1, -.01, -1, -.01), # b1*x1 + ...
                    seed_z=c(2, 0.5, -.03), # b1 + b2*z + b2*z^2
                    seed_x=c(1, -.1, 1, -.1), # b1*x1 + ...
                    rcr_z=c(1.5, 0.4), # N(mean=rcrt1, sd=rcrt2)
                    p_est=0.02, # p(establishment)
                    rcr_SB=0.4, # p(recruit from seedbank)
                    rcr_dir=0.5, # p(recruit directly)
                    s_SB=0.3 # p(survive in seedbank additional year)
                    ))
```

@@

# life history functions
z_pow <- function(z.vec, n_z) {
  if(n_z==1) {
    return(matrix(1, ncol=1, nrow=length(z.vec)))
  } else {
    z <- matrix(z.vec, nrow=length(z.vec), ncol=n_z-1)
    for(i in 1:(n_z-1)) z[,i] <- z[,i]^i
    z <- cbind(1, z)
    return(z)
  }
}
calc_surv <- function(z.v, p, n_sz, X.s) {
  z <- z_pow(z.v, n_sz)
  u <- exp(z %*% p$s_z + c(t(X.s) %*% p$s_x))
  return(u / (1+u))
}
calc_grow <- function(z1, z.v, p, n_gz, X.g) {
  z <- z_pow(z.v, n_gz)
  g <- dnorm(z1, mean=z %*% p$g_z + c(t(X.g) %*% p$g_x), 
             sd=p$g_sig)
  return(g)
}
calc_flwr <- function(z.v, p, n_flz, X.fl) {
  z <- z_pow(z.v, n_flz)
  u <- exp(z %*% p$fl_z + c(t(X.fl) %*% p$fl_x))
  return(u / (1+u))
}
calc_rcrDir <- function(z1, z.v, p, n_seedz, n_flz, X.seed, X.fl) {
  z <- z_pow(z.v, n_seedz)
  calc_flwr(z.v, p, n_flz, X.fl) *
    exp(z %*% p$seed_z + c(t(X.seed) %*% p$seed_x)) *
    p$rcr_dir * 
    p$p_est * 
    dnorm(z1, p$rcr_z[1], p$rcr_z[2])
}
calc_rcrSB <- function(z1, p) {
  p$s_SB * dnorm(z1, p$rcr_z[1], p$rcr_z[2])
}
calc_addSB <- function(z.v, p, n_seedz, n_flz, X.seed, X.fl) {
  z <- z_pow(z.v, n_seedz)
  calc_flwr(z.v, p, n_flz, X.fl) *
    exp(z %*% p$seed_z + c(t(X.seed) %*% p$seed_x)) *
    (1 - p$rcr_dir) *
    p$s_SB
}
calc_staySB <- function(p) {
  p$s_SB * (1 - p$rcr_SB)
}

########
## loop through cells
########
for(i in 1:n.cell) {
  d[[i]] <- data.frame(size=runif(n=n_i[i], min=1, max=12))
  lo <- min(d[[i]]$size)*0.8
  hi <- max(d[[i]]$size)*1.1
  size.mx <- cbind(1, d[[i]]$size, d[[i]]$size^2, d[[i]]$size^3)

@@

  ## recruits
  rcrt.n <- max((sum(d[[i]]$seed, na.rm=TRUE) * p$rcr_dir +
                   B[i] * p$rcr_SB) * p$p_est, 
                2) # need ≥ 2 for IPMpack estimate of rcr_z'_mn, rcr_z'_sd
  rcrt.i <- (n_i[i]+1):(n_i[i]+rcrt.n)
  d[[i]][rcrt.i,] <- NA
  d[[i]]$sizeNext[rcrt.i] <- rnorm(rcrt.n, p$rcr_z[1], p$rcr_z[2])

@@

  # ## IPMpack: estimate slopes from d[[i]]
  # ### set up seedbank transitions
  # d[[i]]$stage <- d[[i]]$stageNext <- "continuous"
  # d[[i]]$stage[is.na(d[[i]]$size)] <- NA
  # d[[i]]$stageNext[d[[i]]$surv==0] <- "dead"
  # d[[i]]$number <- 1 
  # seedbank <- data.frame(size=NA, surv=1, sizeNext=NA,
  #                        fl=NA, seed=NA, 
  #                        stage=c("seedbank", "seedbank", "continuous"),
  #                        stageNext=c("seedbank", "continuous", "seedbank"),
  #                        number=c(p$s_SB, p$rcr_SB*p$p_est, (1-p$rcr_dir)))
  # d[[i]] <- rbind(d[[i]], seedbank)
  # d[[i]]$stage <- as.factor(d[[i]]$stage)
  # d[[i]]$stageNext <- as.factor(d[[i]]$stageNext)
  ### construct kernels
  so <- makeSurvObj(d[[i]], surv ~ size)
  go <- makeGrowthObj(d[[i]], sizeNext ~ size + size2)
  fo <- makeFecObj(d[[i]],
                   Formula=c(fl~size+size2, seed~size+size2),
                   Family=c("binomial", "poisson"),
                   Transform=c("none", "none"),
                   # meanOffspringSize=mean(
                   #   d[[i]]$sizeNext[is.na(d[[i]]$size) &
                   #                     !is.na(d[[i]]$sizeNext)]),
                   # sdOffspringSize=sd(
                   #   d[[i]]$sizeNext[is.na(d[[i]]$size) &
                   #                     !is.na(d[[i]]$sizeNext)]),
                   fecConstants=data.frame(seedlingEstablishmentRate=p$p_est)#,
                   # offspringSplitter=data.frame(seedbank=(1-p$rcr_dir),
                   #                              continuous=p$rcr_dir)
                   )
  F.mx2 <- makeIPMFmatrix(fecObj=fo, minSize=lo, maxSize=hi,
                          correction="constant")
  # D.mx2 <- makeDiscreteTrans(d[[i]])
  # dummy <- as.matrix(fo@offspringRel$coefficients[1], list(1, "seedbank"))
  # D.mx2@meanToCont <- as.matrix(dummy, dimnames=c(1, "seedbank"))
  # dummy <- as.matrix(fo@sdOffspringSize, dimnames=list(1, "seedbank"))
  # D.mx2@sdToCont <- as.matrix(dummy, dimnames=c(1, "seedbank"))
  # D.mx2@discreteTrans[1,1] <- p$s_SB 
  # D.mx2@discreteTrans[3,1] <- 1 - sum(D.mx2@discreteTrans[1:2,1])
  P.mx2 <- makeIPMPmatrix(growObj=go, survObj=so, #discreteTrans=D.mx2,
                            minSize=lo, maxSize=hi, correction="constant")
  IPM2 <- P.mx2 + F.mx2

@@

  # Plots
  z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
  if(regPlots) {
    par(mfrow=c(3,2), mar=c(4,4,2,1))
    xx <- tibble(size=seq(lo, hi, length.out=100), size2=size^2, size3=size^3)
    plot(surv~size, data=d[[i]], ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      points(z.t$size, E_surv, cex=0.2, col="red")
      lines(xx$size, predict(so@fit, xx, type="response"), col="blue")
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      points(z.t$size, E_grow, cex=0.2, col="red")
      lines(xx$size, predict(go@fit, xx, type="response"), col="blue")
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      points(z.t$size, E_fl, cex=0.2, col="red")
      lines(xx$size, predict(fo@fitFec[[1]], xx, type="response"), col="blue")
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      points(z.t$size, E_seed, cex=0.2, col="red")
      lines(xx$size, predict(fo@fitFec[[2]], xx, type="response"), col="blue")
    w1 <- Re(eigen(IPM)$vectors[,1]); stable.dist1 <- w1/sum(w1)
    w2 <- Re(eigen(IPM2)$vectors[,1]); stable.dist2 <- w2/sum(w2)
    yl <- range(c(stable.dist1, stable.dist2))
    plot(y, stable.dist1, ylab="", type="l", lwd=2, col="red", ylim=yl,
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    lines(y, stable.dist2, col="blue")
    # plot(y, S.v); points(y, apply(P.mx, 2, sum), col="red", type="l")
    hist(d[[i]]$sizeNext[rcrt.i], main=paste("Recruit sizes:", main.i), 
         xlab="Recruit size (t+1)", col="grey", freq=FALSE)
      xxx <- seq(0, hi*.5, length.out=100)
      rcrt.z <- d[[i]]$sizeNext[is.na(d[[i]]$size) & !is.na(d[[i]]$sizeNext)]
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red", lwd=2)
      lines(xxx, dnorm(xxx, mean(rcrt.z), sd(rcrt.z)), col="blue")
  }
  if(ipmPlots) {
    par(mfrow=c(2,2), mar=c(4,4,2,1)); main.i <- paste("Cell", i)
    if(length(y) != nrow(IPM)) {
      x <- c(0, y)
    } else {
      x <- y
    }
    # sens.mx <- sens(IPM2); elas.mx <- elas(IPM2)
    sens.mx <- sens(IPM); elas.mx <- elas(IPM)
    image.plot(x, x, t(IPM), main=main.i, xlab="Size (t)", ylab="Size (t+1)")
      points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2))
      abline(a=0, b=1, col="white", lty=2)
    image.plot(P.mx2@meshpoints, P.mx2@meshpoints, t(IPM2), 
               main=main.i, xlab="Size (t)", ylab="Size (t+1)")
      points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2))
      abline(a=0, b=1, col="white", lty=2)
    image.plot(x, x, t(sens.mx),
               main=paste("Sens:", main.i), xlab="Size (t)", ylab="Size (t+1)")
    image.plot(x, x, t(elas.mx),
               main=paste("Elas:", main.i), xlab="Size (t)", ylab="Size (t+1)")
  }
  if(i %% 100 == 0) cat("Finished cell", i, "\n")
}
lam.df <- env.df %>% add_column(lambda=lambdas, lambda2=lambdas2)
ggplot(lam.df, aes(x=x, y=y, fill=log(lambdas))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", 
                       midpoint=0, limits=log(range(c(lambdas, lambdas2))))
ggplot(lam.df, aes(x=x, y=y, fill=log(lambdas2))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", 
                       midpoint=0, limits=log(range(c(lambdas, lambdas2))))
par(mfrow=c(2,2))
plot(log(lambdas) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambdas) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambdas), log(lambdas2)); abline(v=0, h=0, a=0, b=1, lty=c(3,2,2))
plot(density(log(lambdas))); abline(v=0, col="red", lty=2)
```

>>>>

## Species description: Life history, characteristics, relevant attributes
The simulated species is fully described here. The object `sp_i` is a list containing elements for the global parameters, relationships with environmental variables, and demographic matrices that are applicable or potentially applicable for that modeling strategy. Parameters are abbreviated with the associated kernel component (e.g., `s_*` for survival, `g_*` for growth, etc) and the type of covariate (`*_z` for size, `*_x` for environmental covariates).
```{r sp_i}
#set.seed(20)
subsamp <- 20
mean_abund <- 500
regPlots <- T
ipmPlots <- T
if(is.na(subsamp)) { cells <- 1:n_distinct(lc.df$CellID)
} else { cells <- sample(1:n_distinct(lc.df$CellID), subsamp, replace=FALSE) }
n.cell <- length(cells)
n_i <- rpois(n.cell, mean_abund)
sp_i <- list(p=list(s_z=c(-1.75, .75), # b1 + b2*z
                    s_x=c(1, -.1, -.5, -.1), # b1*x1 + ...
                    g_z=c(.2, 2, -0.1), # b1 + b2*z + b3*z^2
                    g_x=c(1, -.1, 1.5, -.1), #b1*x1 + ...
                    g_sig=1, # growth ~ N(E, g_sig)
                    fl_z=c(-1.5, .1, .1), # b1 + b2*z + b3*z^2 + b4*z^3
                    fl_x=c(1, -.01, -1, -.01), # b1*x1 + ...
                    seed_z=c(2, 0.5, -.03), # b1 + b2*z + b2*z^2
                    seed_x=c(1, -.1, 1, -.1), # b1*x1 + ...
                    rcr_z=c(1.5, 0.4), # N(mean=rcrt1, sd=rcrt2)
                    p_est=0.02, # p(establishment)
                    rcr_SB=0.01, # p(recruit from seedbank)
                    rcr_dir=0.95, # p(recruit directly)
                    s_SB=0.01 # p(survive in seedbank additional year)
                    ))
```

@@

# life history functions
z_pow <- function(z.vec, n_z) {
  if(n_z==1) {
    return(matrix(1, ncol=1, nrow=length(z.vec)))
  } else {
    z <- matrix(z.vec, nrow=length(z.vec), ncol=n_z-1)
    for(i in 1:(n_z-1)) z[,i] <- z[,i]^i
    z <- cbind(1, z)
    return(z)
  }
}
calc_surv <- function(z.v, p, n_sz, X.s) {
  z <- z_pow(z.v, n_sz)
  u <- exp(z %*% p$s_z + c(t(X.s) %*% p$s_x))
  return(u / (1+u))
}
calc_grow <- function(z1, z.v, p, n_gz, X.g) {
  z <- z_pow(z.v, n_gz)
  g <- dnorm(z1, mean=z %*% p$g_z + c(t(X.g) %*% p$g_x), 
             sd=p$g_sig)
  return(g)
}
calc_flwr <- function(z.v, p, n_flz, X.fl) {
  z <- z_pow(z.v, n_flz)
  u <- exp(z %*% p$fl_z + c(t(X.fl) %*% p$fl_x))
  return(u / (1+u))
}
calc_rcrDir <- function(z1, z.v, p, n_seedz, n_flz, X.seed, X.fl) {
  z <- z_pow(z.v, n_seedz)
  calc_flwr(z.v, p, n_flz, X.fl) *
    exp(z %*% p$seed_z + c(t(X.seed) %*% p$seed_x)) *
    p$rcr_dir * 
    p$p_est * 
    dnorm(z1, p$rcr_z[1], p$rcr_z[2])
}
calc_rcrSB <- function(z1, p) {
  p$s_SB * p$p_est * dnorm(z1, p$rcr_z[1], p$rcr_z[2])
}
calc_addSB <- function(z.v, p, n_seedz, n_flz, X.seed, X.fl) {
  z <- z_pow(z.v, n_seedz)
  calc_flwr(z.v, p, n_flz, X.fl) *
    exp(z %*% p$seed_z + c(t(X.seed) %*% p$seed_x)) *
    (1 - p$rcr_dir) *
    p$s_SB
}
calc_staySB <- function(p) {
  p$s_SB * (1 - p$rcr_SB)
}

########
## loop through cells
########
for(i in 1:n.cell) {
  d[[i]] <- data.frame(size=runif(n=n_i[i], min=1, max=12))
  lo <- min(d[[i]]$size)*0.75
  hi <- max(d[[i]]$size)*1.25
  size.mx <- cbind(1, d[[i]]$size, d[[i]]$size^2, d[[i]]$size^3)

@@

  ## recruits
  rcrt.n <- max((sum(d[[i]]$seed, na.rm=TRUE) * p$rcr_dir * p$p_est +
                   B[i] * p$rcr_SB * p$p_est), 
                2) # need ≥ 2 for IPMpack estimate of rcr_z'_mn, rcr_z'_sd
  rcrt.i <- (n_i[i]+1):(n_i[i]+rcrt.n)
  d[[i]][rcrt.i,] <- NA
  d[[i]]$sizeNext[rcrt.i] <- rnorm(rcrt.n, p$rcr_z[1], p$rcr_z[2])

@@

  # ## IPMpack: estimate slopes from d[[i]]
  # ### set up seedbank transitions
  d[[i]]$stage <- d[[i]]$stageNext <- "continuous"
  d[[i]]$stage[is.na(d[[i]]$size)] <- NA
  d[[i]]$stageNext[d[[i]]$surv==0] <- "dead"
  d[[i]]$number <- 1
  seedbank <- data.frame(size=NA, surv=1, sizeNext=NA,
                         fl=NA, seed=NA,
                         stage=c("seedbank", "seedbank", "continuous"),
                         stageNext=c("seedbank", "continuous", "seedbank"),
                         number=c(p$s_SB * (1 - p$rcr_SB), 
                                  p$rcr_SB * p$p_est, 
                                  (1 - p$rcr_dir) * p$s_SB))
  d[[i]] <- rbind(d[[i]], seedbank)
  d[[i]]$stage <- as.factor(d[[i]]$stage)
  d[[i]]$stageNext <- as.factor(d[[i]]$stageNext)
  ### construct kernels
  so <- makeSurvObj(d[[i]], surv ~ size)
  go <- makeGrowthObj(d[[i]], sizeNext ~ size + size2)
  fo <- makeFecObj(d[[i]],
                   Formula=c(fl~size+size2, seed~size+size2),
                   Family=c("binomial", "poisson"),
                   Transform=c("none", "none"),
                   meanOffspringSize=mean(
                     d[[i]]$sizeNext[is.na(d[[i]]$size) &
                                       !is.na(d[[i]]$sizeNext)]),
                   sdOffspringSize=sd(
                     d[[i]]$sizeNext[is.na(d[[i]]$size) &
                                       !is.na(d[[i]]$sizeNext)]),
                   fecConstants=data.frame(seedlingEstablishmentRate=p$p_est),
                   offspringSplitter=data.frame(seedbank=(1-p$rcr_dir),
                                                continuous=p$rcr_dir)
                   )
  F.mx2 <- makeIPMFmatrix(fecObj=fo, minSize=lo, maxSize=hi,
                          correction="constant")
  D.mx2 <- makeDiscreteTrans(d[[i]], 
                             continuousToDiscreteExplanatoryVariables=1)
  dummy <- as.matrix(fo@offspringRel$coefficients[1], list(1, "seedbank"))
  D.mx2@meanToCont <- as.matrix(dummy, dimnames=c(1, "seedbank"))
  dummy <- as.matrix(fo@sdOffspringSize, dimnames=list(1, "seedbank"))
  D.mx2@sdToCont <- as.matrix(dummy, dimnames=c(1, "seedbank"))
  D.mx2@discreteTrans[1,1] <- p$s_SB * (1 - p$rcr_SB)
  D.mx2@discreteTrans[3,1] <- 1 - sum(D.mx2@discreteTrans[1:2,1])
  P.mx2 <- makeIPMPmatrix(growObj=go, survObj=so, discreteTrans=D.mx2,
                            minSize=lo, maxSize=hi, correction="constant")
  IPM2 <- P.mx2 + F.mx2

@@

  # Plots
  z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
  if(regPlots) {
    par(mfrow=c(3,2), mar=c(4,4,2,1))
    xx <- tibble(size=seq(lo, hi, length.out=100), size2=size^2, size3=size^3)
    plot(surv~size, data=d[[i]], ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      points(z.t$size, E_surv, cex=0.2, col="red")
      lines(xx$size, predict(so@fit, xx, type="response"), col="blue")
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      points(z.t$size, E_grow, cex=0.2, col="red")
      lines(xx$size, predict(go@fit, xx, type="response"), col="blue")
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      points(z.t$size, E_fl, cex=0.2, col="red")
      lines(xx$size, predict(fo@fitFec[[1]], xx, type="response"), col="blue")
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      points(z.t$size, E_seed, cex=0.2, col="red")
      lines(xx$size, predict(fo@fitFec[[2]], xx, type="response"), col="blue")
    w1 <- Re(eigen(IPM)$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    w2 <- Re(eigen(IPM2)$vectors[,1])[-1]; stable.dist2 <- w2/sum(w2)
    yl <- range(c(stable.dist1, stable.dist2))
    plot(y, stable.dist1, ylab="", type="l", lwd=2, col="red", ylim=yl,
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    lines(y, stable.dist2, col="blue")
    hist(d[[i]]$sizeNext[rcrt.i], main=paste("Recruit sizes:", main.i), 
         xlab="Recruit size (t+1)", col="grey", freq=FALSE)
      xxx <- seq(0, hi*.5, length.out=100)
      rcrt.z <- d[[i]]$sizeNext[is.na(d[[i]]$size) & !is.na(d[[i]]$sizeNext)]
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red", lwd=2)
      lines(xxx, dnorm(xxx, mean(rcrt.z), sd(rcrt.z)), col="blue")
  }
  if(ipmPlots) {
    par(mfrow=c(2,2), mar=c(4,4,2,1)); main.i <- paste("Cell", i)
    if(length(y) != nrow(IPM)) {
      x <- c(0, y)
    } else {
      x <- y
    }
    z.t$z_int <- findInterval(z.t$size, y, all.inside=TRUE)
    z.t$y <- y[z.t$z_int]
    totSeeds <- z.t %>% group_by(y) %>% summarise(seed=sum(seed, na.rm=TRUE))
    sens.mx <- sens(IPM); elas.mx <- elas(IPM)
    image.plot(x, x, t(P.mx), main=paste("P:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
      points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2))
      abline(a=0, b=1, col="white", lty=2)
    image.plot(x, x, t(F.mx), main=paste("F:", main.i), 
               xlab="Size (t)", ylab="Size (t+1)")
      points(totSeeds$y, totSeeds$seed/max(totSeeds$seed)*hi*.9, pch=19)
    image.plot(x, x, t(sens.mx),
               main=paste("Sens:", main.i), xlab="Size (t)", ylab="Size (t+1)")
    image.plot(x, x, t(elas.mx),
               main=paste("Elas:", main.i), xlab="Size (t)", ylab="Size (t+1)")
  }
  if(i %% 100 == 0) cat("Finished cell", i, "\n")
}
lam.df <- env.df %>% add_column(lambda=lambdas, lambda2=lambdas2)
ggplot(lam.df, aes(x=x, y=y, fill=log(lambdas))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", 
                       midpoint=0, limits=log(range(c(lambdas, lambdas2))))
ggplot(lam.df, aes(x=x, y=y, fill=log(lambdas2))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", 
                       midpoint=0, limits=log(range(c(lambdas, lambdas2))))
par(mfrow=c(2,2))
plot(log(lambdas) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambdas) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambdas), log(lambdas2)); abline(v=0, h=0, a=0, b=1, lty=c(3,2,2))
plot(density(log(lambdas))); abline(v=0, col="red", lty=2)
```
